---
title: "more_noisy_channel"
author: "Zachary Houghton"
date: "2023-12-13"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(profvis)
#nstall.packages("microbenchmark")
library(microbenchmark)
library(furrr)
library(tictoc)
```

## Source our functions:

For an explanation of the function, see the `noisy_channel_sims.rmd` file.

```{r}
source('iterated_learning.R')
```

## Getting to the stationary distribution with gen_pref = 0.6 (varying N)

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 1/100


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

#no_cores = availableCores() - 1
#plan(multisession, workers = no_cores)


#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) # we use purr::pmap_dfr() here to apply our function because it's a bit cleaner (and because I want to practice using that 
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6.csv')


plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

## Getting to the stationary distribution with gen_pref = 0.75 (varying N)

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 1/100


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) #to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75.csv')

new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

## Same as above but with p_noise = 0.1

### genpref = 0.6

```{r message = F, warning = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value
nu = 10
p_noise = 1/10
prior_prob_noise = 1/10


WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

#df = as.data.frame(c(50, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)


#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) # we use purr::pmap_dfr() here to apply our function because it's a bit cleaner (and because I want to practice using that library)
#toc()

new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_0.1.csv')

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

```

### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/10
prior_prob_noise = 1/10

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_0.1.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_0.1.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### Genpref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value
#N = 200
#prior_mu = 0.6
nu = 10
p_noise = 1/10
prior_prob_noise = 1/10


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 3
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = F), 'Overall Frequency' = ..1))

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_0.1.csv')
#test_df = df %>% group_by(word_row) %>% nest()
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_0.1.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))
ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()


```

## P_noise = 0

### Genpref = 0.6

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) 
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6_pnoise_0.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_0.csv')
#test_df = df %>% group_by(word_row) %>% nest()

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_0.csv')

new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_0.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### GenPref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value
#N = 200
#prior_mu = 0.6
nu = 10
p_noise = 0
prior_prob_noise = 0


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_0.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_0.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 
ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

## P_noise = 0.01

### Genpref = 0.6

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 1/100


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

#no_cores = availableCores() - 1
#plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) 
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6_pnoise_.01.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_.01.csv')
#test_df = df %>% group_by(word_row) %>% nest()

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 1/100

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_.01.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_.01.csv')

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### GenPref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value
#N = 200
#prior_mu = 0.6
nu = 10
p_noise = 1/100
prior_prob_noise = 1/100


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_.01.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_.01.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

## P_noise = 0.001

### Genpref = 0.6

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/1000
prior_prob_noise = 1/1000



WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) 
#toc()
#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6_pnoise_.001.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_.001.csv')


plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/1000
prior_prob_noise = 1/1000



WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_.001.csv')

new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_.001.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### GenPref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/1000
prior_prob_noise = 1/1000

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_.001.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_.001.csv')

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

## What if speaker makes no errors

### Genpref = 0.6

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) 
#toc()
#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6_pnoise_.01_producer_nonoise.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_.01_producer_nonoise.csv')

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_.01_producer_nonoise.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_.01_producer_nonoise.csv')

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### GenPref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100
prior_prob_noise = 0


WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()


#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_.01_producer_nonoise.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_.01_producer_nonoise.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

### P_noise = 0

#### Genpref = 0.6

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1)) 
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.6_pnoise_0_producer_nonoise.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.6_pnoise_0_producer_nonoise.csv')
#test_df = df %>% group_by(word_row) %>% nest()

plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


ggplot(data = plot_data, aes(x = posterior_mu)) +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  #geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1)) +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  theme_bw() +
  theme(axis.title = element_text(size = 12))

#ggsave('./Write-up/Figures/noNoise.png', width = 20, height = 7, units = 'cm')
```

#### Genpref = 0.75

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0
prior_prob_noise = 0

WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.75

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.75_pnoise_0_producer_nonoise.csv')

new_df = read_csv('../Sims Data/nsims_1000_genpref_0.75_pnoise_0_producer_nonoise.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df #%>%
  #filter(generation == 1000)

ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

#### GenPref = 0.5

```{r warning = F, message = F}
n_gen = 500
n_sims = 1000
p_theta = 0.5 #initial p_theta value
#N = 200
#prior_mu = 0.6
nu = 10
p_noise = 0
prior_prob_noise = 0


#N = 100
WordA = 'WordA'
WordB = 'WordB'
prior_mu = 0.5

df = as.data.frame(c(50, 500, 1000, 10000))


no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

#tic()
#new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))# to practice using that library)
#toc()

#write_csv(new_df, '../Sims Data/nsims_1000_genpref_0.5_pnoise_0_producer_nonoise.csv')
new_df = read_csv('../Sims Data/nsims_1000_genpref_0.5_pnoise_0_producer_nonoise.csv')
plot_data = new_df #%>%
  #filter(generation %in% c(1,100,500))
  #ungroup() %>%
  #filter(word_row %in% sample(1:nrow(data_sliced), size = 6))

ggplot(data = plot_data, aes(x = estimated_p_theta, y = posterior_mu)) +
  geom_point(alpha = 0.1) +
  facet_grid(generation ~ `Overall.Frequency`) +
  theme_bw()


density_plot_data = new_df 
ggplot(data = density_plot_data, aes(x = posterior_mu)) +
  geom_density() +
  theme_bw()

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()
```

```{r}

```

