---
title: "Speaker vs Listener Noise Ratios"
author: "Zach"
date: "2024-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(profvis)
#nstall.packages("microbenchmark")
library(microbenchmark)
library(furrr)
library(tictoc)
library(ggpubr)
source('iterated_learning.R')
library(grid)
library(ggh4x)
```

## Speaker vs Listener Noise

In this section we'll manipulate the relationship between speaker (prior_noise) and listener (p_noise).

### p_noise = 0.01, prior_noise = 0.001

We'll keep p_theta equal to 0.5 and prior_mu equal to 0.6.

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100 #listener noise
prior_prob_noise = 1/1000 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.001_listener_.01.csv'

if (!file.exists(file_path)) {

new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.001_listener_.01.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.001_listener_.01.csv')
}

plot_data = new_df 
freq_labs = c('N = 50', 'N=100', 'N=500', 'N=1000', 'N=10000')
p_higher_reg = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()

p_higher_reg

ggarrange(p_lower_reg, p_higher_reg, ncol = 1)
#ggsave('./Write-up/Figures/higher_and_lower_reg.png')
#ggsave('./Write-up/Figures/speaker_noise_001_listener_01.png', width = 20, height = 7, units = 'cm')
```

### p_noise = 0.001, prior_noise = 0.01

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/1000 #listener noise
prior_prob_noise = 1/100 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.001.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.001.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.001.csv')
}

plot_data = new_df 

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  #geom_density() +
  facet_wrap(~ Overall.Frequency, nrow = 1) +
  scale_x_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1)) +
  theme_bw()

#ggsave('./Write-up/Figures/speaker_noise_01_listener_001.png', width = 20, height = 7, units = 'cm')
```

### p_noise = 0.1, prior_noise = 0.091

Here we keep the relative difference the same

```{r}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.1 #listener noise
prior_prob_noise = 0.091 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.1_listener_.091.csv'

if (!file.exists(file_path)) {

new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.1_listener_.091.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.1_listener_.091.csv')
}

plot_data = new_df 

rel_dif2 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~ Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1.0), limits = c(-0.1, 1.1)) +
  theme_bw()


ggarrange(rel_dif2, p_higher_reg, nrow = 2)
#ggsave('./Write-up/Figures/absolute_matters.png', width = 20, height = 14, units = 'cm')
```

### p_noise = 0.1, prior_noise = 0.01

Here, p_noise is still 10x greater than prior_noise, but the relative difference is different:

```{r}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.1 #listener noise
prior_prob_noise = 1/100 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.1_listener_.01.csv'

if (!file.exists(file_path)) {

new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.1_listener_.01.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.1_listener_.01.csv')
}

plot_data = new_df 

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  xlab(expression(mu[posterior]))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()

#ggsave('./Write-up/Figures/speaker_noise_01_listener_1.png')
```

### p_noise = 0.05, prior_noise = 0.01

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/20 #listener noise
prior_prob_noise = 1/100 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.05.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.05.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.05.csv')
}

plot_data = new_df 

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

```

### p_noise = 0.01, prior_noise = 0.05

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 1/100 #listener noise
prior_prob_noise = 1/20 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.05_listener_.01.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.05_listener_.01.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.05_listener_.01.csv')
}


plot_data = new_df 

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram() +
  geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  theme_bw()

```

So clearly we get regularization when the listener assumes greater noise than the speaker produces. Let's try a few simulations where the difference is small:

### p_noise = 0.01, prior_noise = 0.005

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.005 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.005.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.005.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.005.csv')
}


plot_data = new_df 

p_lower_reg = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  xlab(expression(mu[posterior]))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()

```

### p_noise = 0.01, prior_noise = 0.009

```{r warning = F, message = F}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.009 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.009.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.009.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.009.csv')
}


plot_data = new_df 

ngen_500_2 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()
```

What if we have the same noise level but 1000 generations? (Maybe it takes longer to get to the stable generation with such a small difference between speaker and listener noise levels.

```{r warning = F, message = F}
n_gen = 1000 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.009 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.009_ngen1000.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.009_ngen1000.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.009_ngen1000.csv')
}


plot_data = new_df 

ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  xlab(expression(mu[posterior]))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()

```

### p_noise = 0.01, prior_noise = 0.0075

```{r}
n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.0075.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.0075.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.0075.csv')
}


plot_data = new_df 

ngen_500 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0.5, 1)) +
  theme_bw()
```

### 2000 generations

Since it seems like these eventually regularize, let's confirm this by trying a simulation with 2000 generations.

```{r warning = F, message = F}
n_gen = 2000 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.009 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.009_ngen2000.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.009_ngen2000.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.009_ngen2000.csv')
}


plot_data = new_df 

ngen_2000_2 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0.5, 1)) +
  theme_bw()
```

```{r}
n_gen = 6000 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.009 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.009_ngen6000.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.009_ngen6000.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.009_ngen6000.csv')
}


plot_data = new_df 

ngen_2000_3 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0.5, 1)) +
  theme_bw()

ggarrange(ngen_2000_2, ngen_2000_3)
```

```{r warning = F, message = F}
n_gen = 2000 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.0075_ngen2000.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.0075_ngen2000.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.0075_ngen2000.csv')
}


plot_data = new_df 

ngen_2000 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_wrap(~Overall.Frequency, nrow = 1) +
  xlab(bquote(P(S[i])))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0.5, 1)) +
  theme_bw()

ggarrange(ngen_2000_2, ngen_2000, nrow = 2)

#ggsave('./Write-up/Figures/fasterSlowerReg.png', , width = 20, height = 14, units = 'cm')
```

```{r}
n_gen = 2000 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
p_noise = 0.01 #listener noise
prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/speaker_.01_listener_.0075_ngen2000.csv'

if (!file.exists(file_path)) {


new_df = pmap_dfr(df, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = p_noise, prior_prob_noise = prior_prob_noise, last_gen_only = T), 'Overall Frequency' = ..1))

write_csv(new_df, '../Sims Data/speaker_.01_listener_.0075_ngen2000.csv')

} else {
new_df = read_csv('../Sims Data/speaker_.01_listener_.0075_ngen2000.csv')
}


plot_data = new_df 

ngen_2000 = ggplot(data = plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  #geom_density() +
  facet_grid(generation ~ Overall.Frequency) +
  xlab(expression(mu[posterior]))+
  ylab('Density') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  theme_bw()
```

# Big Graph

```{r}
N = c(100, 1000, 10000)
speaker_noise = seq(0, 0.1, by = 0.02)
listener_noise = speaker_noise

combinations = expand.grid(N, speaker_noise, listener_noise)

colnames(combinations) = c('N', 'listener_noise', 'speaker_noise')

n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
#p_noise = 0.01 #listener noise
#prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/full_graph.csv'


if (!file.exists(file_path)) {


new_df = pmap_dfr(combinations, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = ..2, prior_prob_noise = ..3, last_gen_only = T), 'Overall Frequency' = ..1, 'p_noise' = ..2, 'prior_prob_noise' = ..3))

write_csv(new_df, file_path)

} else {
new_df = read_csv(file_path)
}


plot_data = new_df 



n_labs = c('N = 100', 'N = 1000', 'N = 10000')
#prior_prob_noise_labs = c(bquote(P[noise] = 0), bquote(P[noise] = 0.02), bquote(P[noise] = 0.04), bquote(P[noise] = 0.06), bquote(P[noise] = 0.08), bquote(P[noise] = 0.1))

plot_data$Overall.Frequency = factor(plot_data$Overall.Frequency, levels = c('100', '1000', '10000'),
                                     labels = c('N == 100', 'N == 1000', 'N == 10000'))

plot_data$p_noise = factor(plot_data$p_noise, levels = c('0', '0.02', '0.04', '0.06', '0.08', '0.1'),
                           labels = c('P[noise] == 0', 'P[noise] == 0.02', 'P[noise] == 0.04', 'P[noise] == 0.06', 'P[noise] == 0.08', 'P[noise] == 0.1'))

plot_data$prior_prob_noise = factor(plot_data$prior_prob_noise, levels = c('0', '0.02', '0.04', '0.06', '0.08', '0.1'),
                           labels = c('P[SpeakerNoise] == 0', 'P[SpeakerNoise] == 0.02', 'P[SpeakerNoise] == 0.04', 'P[SpeakerNoise] == 0.06', 'P[SpeakerNoise] == 0.08', 'P[SpeakerNoise] == 0.1'))

#names(n_labs) = c('100', '1000', '10000')
#names(prior_prob_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')
#names(p_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')


full_plot = ggplot(plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  facet_nested(p_noise ~prior_prob_noise + Overall.Frequency,
             labeller = label_parsed) + #speaker noise and N on x-axis, listener noise on y-axis
  ylab('Density') +
  xlab(bquote(P(S[i]))) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c('0', '0.5', '1')) +
  theme_bw() +
  theme(strip.text = element_text(
    size = 15, color = "black"),
        axis.title = element_text(size = 15)) #+
  #theme_bw()
  
full_plot

gt = ggplot_gtable(ggplot_build(full_plot))
#gtable_show_layout(gt)

#gt$heights[8] = 1.2 * gt$heights[7]
#gt$heights[10] = 1.2 * gt$heights[7]
#gt$heights[12] = 1.2 * gt$heights[7]
#gt$heights[14] = 1.2 * gt$heights[7]
#gt$heights[16] = 1.2 * gt$heights[7]
#gt$heights[18] = 1.2 * gt$heights[7]
gt$widths[15] = 4*gt$widths[15]
gt$widths[27] = 4*gt$widths[27]
gt$widths[39] = 4*gt$widths[39]
gt$widths[51] = 4*gt$widths[51]
gt$widths[63] = 4*gt$widths[63]
gt$widths[75] = 4*gt$widths[75]
grid.draw(gt)
```

# Big Graph Ordered

```{r warning=F}
N = c(100, 1000, 10000)
speaker_noise = seq(0, 0.1, by = 0.02)
listener_noise = speaker_noise

combinations = expand.grid(N, speaker_noise, listener_noise)

colnames(combinations) = c('N', 'listener_noise', 'speaker_noise')

n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
#p_noise = 0.01 #listener noise
#prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/full_graph_ordered.csv'


if (!file.exists(file_path)) {


new_df = pmap_dfr(combinations, ~data.frame(iterated_learning_ordered(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = ..2, prior_prob_noise = ..3, last_gen_only = T), 'Overall Frequency' = ..1, 'p_noise' = ..2, 'prior_prob_noise' = ..3))

write_csv(new_df, file_path)

} else {
new_df = read_csv(file_path)
}


plot_data = new_df 



n_labs = c('N = 100', 'N = 1000', 'N = 10000')
#prior_prob_noise_labs = c(bquote(P[noise] = 0), bquote(P[noise] = 0.02), bquote(P[noise] = 0.04), bquote(P[noise] = 0.06), bquote(P[noise] = 0.08), bquote(P[noise] = 0.1))

plot_data$Overall.Frequency = factor(plot_data$Overall.Frequency, levels = c('100', '1000', '10000'),
                                     labels = c('N == 100', 'N == 1000', 'N == 10000'))

plot_data$p_noise = factor(plot_data$p_noise, levels = c('0', '0.02', '0.04', '0.06', '0.08', '0.1'),
                           labels = c('P[noise] == 0', 'P[noise] == 0.02', 'P[noise] == 0.04', 'P[noise] == 0.06', 'P[noise] == 0.08', 'P[noise] == 0.1'))

plot_data$prior_prob_noise = factor(plot_data$prior_prob_noise, levels = c('0', '0.02', '0.04', '0.06', '0.08', '0.1'),
                           labels = c('P[SpeakerNoise] == 0', 'P[SpeakerNoise] == 0.02', 'P[SpeakerNoise] == 0.04', 'P[SpeakerNoise] == 0.06', 'P[SpeakerNoise] == 0.08', 'P[SpeakerNoise] == 0.1'))

#names(n_labs) = c('100', '1000', '10000')
#names(prior_prob_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')
#names(p_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')


full_plot = ggplot(plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  facet_nested(p_noise ~prior_prob_noise + Overall.Frequency,
             labeller = label_parsed) + #speaker noise and N on x-axis, listener noise on y-axis
  ylab('Density') +
  xlab(bquote(P(S[i]))) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c('0', '0.5', '1')) +
  theme_bw() +
  theme(strip.text = element_text(
    size = 15, color = "black"),
        axis.title = element_text(size = 15)) #+
  #theme_bw()
  
full_plot

gt = ggplot_gtable(ggplot_build(full_plot))
#gtable_show_layout(gt)

#gt$heights[8] = 1.2 * gt$heights[7]
#gt$heights[10] = 1.2 * gt$heights[7]
#gt$heights[12] = 1.2 * gt$heights[7]
#gt$heights[14] = 1.2 * gt$heights[7]
#gt$heights[16] = 1.2 * gt$heights[7]
#gt$heights[18] = 1.2 * gt$heights[7]
gt$widths[15] = 4*gt$widths[15]
gt$widths[27] = 4*gt$widths[27]
gt$widths[39] = 4*gt$widths[39]
gt$widths[51] = 4*gt$widths[51]
gt$widths[63] = 4*gt$widths[63]
gt$widths[75] = 4*gt$widths[75]
grid.draw(gt)
```

# Smaller Big Data

```{r}
N = c(100, 1000, 10000)
speaker_noise = seq(0, 0.1, length.out = 4)
listener_noise = speaker_noise

combinations = expand.grid(N, speaker_noise, listener_noise)

colnames(combinations) = c('N', 'listener_noise', 'speaker_noise')

n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
#p_noise = 0.01 #listener noise
#prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/full_graph_smaller.csv'


if (!file.exists(file_path)) {


new_df = pmap_dfr(combinations, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = ..2, prior_prob_noise = ..3, last_gen_only = T), 'Overall Frequency' = ..1, 'p_noise' = ..2, 'prior_prob_noise' = ..3))

write_csv(new_df, file_path)

} else {
new_df = read_csv(file_path)
}


plot_data = new_df 



n_labs = c('N = 100', 'N = 1000', 'N = 10000')
#prior_prob_noise_labs = c(bquote(P[noise] = 0), bquote(P[noise] = 0.02), bquote(P[noise] = 0.04), bquote(P[noise] = 0.06), bquote(P[noise] = 0.08), bquote(P[noise] = 0.1))

plot_data = plot_data %>%
  mutate_if(is.numeric, round, 4)

plot_data$Overall.Frequency = factor(plot_data$Overall.Frequency, levels = c('100', '1000', '10000'),
                                     labels = c('N == 100', 'N == 1000', 'N == 10000'))

plot_data$p_noise = factor(plot_data$p_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[noise] == 0', 'P[noise] == 0.033', 'P[noise] == 0.066', 'P[noise] == 0.1'))

plot_data$prior_prob_noise = factor(plot_data$prior_prob_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[SpeakerNoise] == 0', 'P[SpeakerNoise] == 0.033', 'P[SpeakerNoise] == 0.066', 'P[SpeakerNoise] == 0.1'))

#names(n_labs) = c('100', '1000', '10000')
#names(prior_prob_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')
#names(p_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')


full_plot = ggplot(plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  facet_nested(p_noise ~ prior_prob_noise + Overall.Frequency,
             labeller = label_parsed) + #speaker noise and N on x-axis, listener noise on y-axis
  ylab('Density') +
  xlab(bquote(P(S[i]))) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c('0', '0.5', '1')) +
  theme_bw() +
  theme(strip.text = element_text(
    size = 11, color = "black"),
        axis.title = element_text(size = 13)) #+
  #theme_bw()
  
full_plot

gt = ggplot_gtable(ggplot_build(full_plot))
#gtable_show_layout(gt)

#gt$heights[8] = 1.2 * gt$heights[7]
#gt$heights[10] = 1.2 * gt$heights[7]
#gt$heights[12] = 1.2 * gt$heights[7]
#gt$heights[14] = 1.2 * gt$heights[7]
#gt$heights[16] = 1.2 * gt$heights[7]
#gt$heights[18] = 1.2 * gt$heights[7]
gt$widths[15] = 4*gt$widths[15]
gt$widths[27] = 4*gt$widths[27]
gt$widths[39] = 4*gt$widths[39]
gt$widths[51] = 4*gt$widths[51]
gt$widths[63] = 4*gt$widths[63]
gt$widths[75] = 4*gt$widths[75]
grid.draw(gt)

ggsave(full_plot, filename = 'full_plot_smaller.png', width = 11, height = 6)
```

# Smaller graph with N 10, 100, 200

```{r warning=F}
N = c(10, 100, 300)
speaker_noise = seq(0, 0.1, length.out = 4)
listener_noise = speaker_noise

combinations = expand.grid(N, speaker_noise, listener_noise)

colnames(combinations) = c('N', 'listener_noise', 'speaker_noise')

n_gen = 500 #number of generations
n_sims = 1000 #number of chains
p_theta = 0.5 #initial p_theta value

nu = 10
#p_noise = 0.01 #listener noise
#prior_prob_noise = 0.0075 #speaker noise

prior_mu = 0.6

#df = as.data.frame(c(50, 100, 500, 1000, 10000))

no_cores = availableCores() - 1
plan(multisession, workers = no_cores)

file_path = '../Sims Data/full_graph_smallerN4.csv'


if (!file.exists(file_path)) {


new_df = pmap_dfr(combinations, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = ..2, prior_prob_noise = ..3, last_gen_only = T), 'Overall Frequency' = ..1, 'p_noise' = ..2, 'prior_prob_noise' = ..3))

write_csv(new_df, file_path)

} else {
new_df = read_csv(file_path)
}


plot_data = new_df 



n_labs = c('N = 10', 'N = 100', 'N = 300')
#prior_prob_noise_labs = c(bquote(P[noise] = 0), bquote(P[noise] = 0.02), bquote(P[noise] = 0.04), bquote(P[noise] = 0.06), bquote(P[noise] = 0.08), bquote(P[noise] = 0.1))

plot_data = plot_data %>%
  mutate_if(is.numeric, round, 4)

plot_data$Overall.Frequency = factor(plot_data$Overall.Frequency, levels = c('10', '100', '300'),
                                     labels = c('N == 10', 'N == 100', 'N == 300'))

plot_data$p_noise = factor(plot_data$p_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[noise] == 0', 'P[noise] == 0.033', 'P[noise] == 0.066', 'P[noise] == 0.1'))

plot_data$prior_prob_noise = factor(plot_data$prior_prob_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[SpeakerNoise] == 0', 'P[SpeakerNoise] == 0.033', 'P[SpeakerNoise] == 0.066', 'P[SpeakerNoise] == 0.1'))

#names(n_labs) = c('100', '1000', '10000')
#names(prior_prob_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')
#names(p_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')


full_plot = ggplot(plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  facet_nested(p_noise ~ prior_prob_noise + Overall.Frequency,
             labeller = label_parsed) + #speaker noise and N on x-axis, listener noise on y-axis
  ylab('Density') +
  xlab(bquote(P(S[i]))) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c('0', '0.5', '1')) +
  theme_bw() +
  theme(strip.text = element_text(
    size = 11, color = "black"),
        axis.title = element_text(size = 13)) #+
  #theme_bw()
  
full_plot

#gt = ggplot_gtable(ggplot_build(full_plot))
#gtable_show_layout(gt)

#gt$heights[8] = 1.2 * gt$heights[7]
#gt$heights[10] = 1.2 * gt$heights[7]
#gt$heights[12] = 1.2 * gt$heights[7]
#gt$heights[14] = 1.2 * gt$heights[7]
#gt$heights[16] = 1.2 * gt$heights[7]
#gt$heights[18] = 1.2 * gt$heights[7]
# gt$widths[15] = 4*gt$widths[15]
# gt$widths[27] = 4*gt$widths[27]
# gt$widths[39] = 4*gt$widths[39]
# gt$widths[51] = 4*gt$widths[51]
# gt$widths[63] = 4*gt$widths[63]
# gt$widths[75] = 4*gt$widths[75]
# grid.draw(gt)

ggsave(full_plot, filename = 'full_plot_smallerN4.png', width = 11, height = 6)
```
```{r}

file_path = '../Sims Data/full_graph_smallerN.csv'


if (!file.exists(file_path)) {


new_df = pmap_dfr(combinations, ~data.frame(iterated_learning(n_gen = n_gen, n_sims = n_sims, p_theta = 0.5, N = ..1, prior_mu = prior_mu, nu = nu, p_noise = ..2, prior_prob_noise = ..3, last_gen_only = T), 'Overall Frequency' = ..1, 'p_noise' = ..2, 'prior_prob_noise' = ..3))

write_csv(new_df, file_path)

} else {
new_df = read_csv(file_path)
}


plot_data = new_df 



n_labs = c('N = 10', 'N = 100', 'N = 1000')
#prior_prob_noise_labs = c(bquote(P[noise] = 0), bquote(P[noise] = 0.02), bquote(P[noise] = 0.04), bquote(P[noise] = 0.06), bquote(P[noise] = 0.08), bquote(P[noise] = 0.1))

plot_data = plot_data %>%
  mutate_if(is.numeric, round, 4)

plot_data$Overall.Frequency = factor(plot_data$Overall.Frequency, levels = c('10', '100', '300'),
                                     labels = c('N == 10', 'N == 100', 'N == 300'))

plot_data$p_noise = factor(plot_data$p_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[noise] == 0', 'P[noise] == 0.033', 'P[noise] == 0.066', 'P[noise] == 0.1'))

plot_data$prior_prob_noise = factor(plot_data$prior_prob_noise, levels = c('0', '0.0333', '0.0667', '0.1'),
                           labels = c('P[SpeakerNoise] == 0', 'P[SpeakerNoise] == 0.033', 'P[SpeakerNoise] == 0.066', 'P[SpeakerNoise] == 0.1'))

#names(n_labs) = c('100', '1000', '10000')
#names(prior_prob_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')
#names(p_noise_labs) = c('0', '0.02', '0.04', '0.06', '0.08', '0.1')


full_plot = ggplot(plot_data, aes(x = posterior_mu, y = ..density..)) +
  geom_histogram(color = 'black', fill = 'white') +
  facet_nested(p_noise ~ prior_prob_noise + Overall.Frequency,
             labeller = label_parsed) + #speaker noise and N on x-axis, listener noise on y-axis
  ylab('Density') +
  xlab(bquote(P(S[i]))) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c('0', '0.5', '1')) +
  theme_bw() +
  theme(strip.text = element_text(
    size = 11, color = "black"),
        axis.title = element_text(size = 13)) #+
  #theme_bw()
  
full_plot

#gt = ggplot_gtable(ggplot_build(full_plot))
#gtable_show_layout(gt)

#gt$heights[8] = 1.2 * gt$heights[7]
#gt$heights[10] = 1.2 * gt$heights[7]
#gt$heights[12] = 1.2 * gt$heights[7]
#gt$heights[14] = 1.2 * gt$heights[7]
#gt$heights[16] = 1.2 * gt$heights[7]
#gt$heights[18] = 1.2 * gt$heights[7]
# gt$widths[15] = 4*gt$widths[15]
# gt$widths[27] = 4*gt$widths[27]
# gt$widths[39] = 4*gt$widths[39]
# gt$widths[51] = 4*gt$widths[51]
# gt$widths[63] = 4*gt$widths[63]
# gt$widths[75] = 4*gt$widths[75]
# grid.draw(gt)

#ggsave(full_plot, filename = 'full_plot_smallerN4.png', width = 11, height = 6)
```

